**Density Dependence**

### 2022-12-13 Rmd/runCond.Rmd
1st Draft

```{r, mac.data}
load("/home/laurie/Dropbox/pelagics/data/om/mac.RData")
ts =as.data.frame(read_excel("/home/laurie/Desktop/projects/ddmse/data/inputs/dat.xlsx",3))

@@

```{r, whb.data}
load("/home/laurie/Dropbox/pelagics/data/om/whb.RData")
ts=model.frame(FLQuants(whb,tb=biomass,ssb=ssb),drop=T)
ts$tb=ts$tb/1e6

>>>>

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel("../data/inputs/dat.xlsx",3))

@@

```{r, whb.data}
load(file.path(dropboxdir,"data/om/whb.RData"))
ts=model.frame(FLQuants(whb,tb=biomass,ssb=ssb),drop=T)
ts$tb=ts$tb/1e6
